Evaluating the Performance and Energy Efficiency of the \textsc{COSMO-ART} model system

### 2014-04-25 trunk/paper_enahpc14/Sec4:Experimental-results.tex
Manuel's changes

>>>>

In order to obtain an initial overview of the power dissipation of the system model, we run a
full-day simulation of \cosmoart and capture the power profiles leveraging the two
stated MPI policies, polling and blocking. Figure~\ref{fig:9} shows the power profiles
of two \cosmoart runs featuring both MPI waiting modes. The first observation is that,
for the polling MPI policy

The first observation is that
